Notes for Week 12/7/19 - 12/29/19

### 2020-01-13 notes/graph_testing_summary.tex
added minimax regression testing rate for higher order Holder classes

We wish to distinguish
\begin{equation*}
\mathbf{H}_0: f = f_0 := 0 \quad \textrm{vs} \quad \mathbf{H}_{\textrm{a}}: f \neq f_0
\end{equation*}
We will evaluate our performance using worst-case risk: for a given function class $\mathcal{H}$ and test function $\phi: \Reals^n \to \set{0,1}$, let
\begin{equation*}
\mathcal{R}(\phi; \mathcal{H}) = \Ebb_{f = f_0}(\phi) + \sup_{f \in \mathcal{H}, f \neq f_0} \Ebb_f(1 - \phi).
\end{equation*}
The worst-case risk may be quite close to $1$ unless we require some separation between null and alternative spaces. A more realistic measure of performance is therefore
\begin{equation*}
\mathcal{R}_{\epsilon}(\phi; \mathcal{H}) = \Ebb_{f = f_0}(\phi) + \sup_{f \in \mathcal{H}, \norm{f - f_0}_2 \geq \epsilon} \Ebb_f(1 - \phi).
\end{equation*}

@@

\begin{theorem}
	\label{thm:sobolev_testing_rate}
	Let $b \geq 1$ and $a > 0$ be fixed constants, and let $d < 4$. Suppose that $\Pbb$ is an absolutely continuous probability measure over $\mathcal{X} = [0,1]^d$ with density function $p$ bounded above and below by constants, i.e
	\begin{equation*}
	0 < p_{\min} < p(x) < p_{\max} < \infty, \quad \textrm{for all $x \in \mathcal{X}$.}
	\end{equation*}
	Then the following statement holds: if the test $\phi_{\spec}$ is performed with parameter choices 
	\begin{equation*}
	r = \log^a n \cdot \left(\frac{\log n}{n}\right)^{1/d}, ~\kappa = n^{2d/(4 + d)}, ~\tau = \frac{\kappa}{n} + b\sqrt{\frac{2\kappa}{n^2}}
	\end{equation*}
	then there exists a constant $c$ which may depend on $d,R,p_{\max},b$ and $a$ but is independent of the sample size $n$ such that for every $\epsilon \geq 0$ satisfying
	\begin{equation}
	\label{eqn:sobolev_testing_rate}
	\epsilon^2 \geq c \cdot b \cdot n^{-4/(4 + d)} (\log n)^{h(a,d)}
	\end{equation}
	the worst-case risk is upper bounded
	\begin{equation}
	\label{eqn:sobolev_testing_rate_1}
	\mathcal{R}_{\epsilon}(\phi_{\mathrm{spec}}; \mathcal{W}^{1,2}(\mathcal{X};R)) \lesssim \frac{1}{b}.
	\end{equation}
\end{theorem}
The testing rate~\eqref{eqn:sobolev_testing_rate} matches the minimax critical radius up to a factor of $\log^{h(a,d)}n$.

>>>>

We wish to distinguish
\begin{equation*}
\mathbf{H}_0: f = f_0 := 0 \quad \textrm{vs} \quad \mathbf{H}_{\textrm{a}}: f \neq f_0
\end{equation*}
We will evaluate our performance using worst-case risk: for a given function class $\mathcal{H}$ and test function $\phi: \Reals^n \to \set{0,1}$, let
\begin{equation*}
\mathcal{R}(\phi; \mathcal{H}) = \Ebb_{f = f_0}(\phi) + \sup_{f \in \mathcal{H}, f \neq f_0} \Ebb_f(1 - \phi).
\end{equation*}
The worst-case risk may be quite close to $1$ unless we enforce some separation between null and alternative spaces. A more realistic measure of performance is therefore
\begin{equation*}
\mathcal{R}_{\epsilon}(\phi; \mathcal{H}) = \Ebb_{f = f_0}(\phi) + \sup_{f \in \mathcal{H}, \norm{f - f_0}_{\Leb^2} \geq \epsilon} \Ebb_f(1 - \phi).
\end{equation*}

@@

\begin{theorem}
	\label{thm:sobolev_testing_rate}
	Let $b \geq 1$ and $a > 0$ be fixed constants, and let $d < 4$. Suppose that $\Pbb$ is an absolutely continuous probability measure over $\mathcal{X} = [0,1]^d$ with density function $p$ bounded above and below by constants, i.e
	\begin{equation*}
	0 < p_{\min} < p(x) < p_{\max} < \infty, \quad \textrm{for all $x \in \mathcal{X}$.}
	\end{equation*}
	Then the following statement holds: if the test $\phi_{\spec}$ is performed with parameter choices 
	\begin{equation*}
	r = \log^a n \cdot \left(\frac{\log n}{n}\right)^{1/d}, ~\kappa = n^{2d/(4 + d)}, ~\tau = \frac{\kappa}{n} + b\sqrt{\frac{2\kappa}{n^2}}
	\end{equation*}
	then there exists a constant $c$ which may depend on $d,R,p_{\max},b$ and $a$ but is independent of the sample size $n$ such that for every $\epsilon \geq 0$ satisfying
	\begin{equation}
	\label{eqn:sobolev_testing_rate}
	\epsilon^2 \geq c \cdot b \cdot n^{-4/(4 + d)} (\log n)^{h(a,d)}
	\end{equation}
	the worst-case risk is upper bounded
	\begin{equation}
	\label{eqn:sobolev_testing_rate_1}
	\mathcal{R}_{\epsilon}(\phi_{\mathrm{spec}}; W^{1,2}(\mathcal{X};R)) \lesssim \frac{1}{b}.
	\end{equation}
\end{theorem}

### 2020-01-13 notes/weekly_notes/12.20.19.NotesForWeek.tex
added minimax regression testing rate for higher order Holder classes

In this week's notes, we will focus our attention on upper bounding the roughness functional $R_{n,s}(f)$. Our main results should take the following form: when (a) $f \in C^{s}(L)$ for a fixed constant $L$ (or more ideally $f \in \mathcal{W}^{s}(L)$), (b) the neighborhood graph radius $r = r(n)$ is properly chosen as a function of $n$, and (c) $K$ is an appropriately chosen kernel, the roughness functional satisfies
\begin{equation}
\label{eqn:roughness_functional_bound}
\mathbb{E}\left[R_{s,n}(f)\right] = O\left(L^2\right)
\end{equation}

These notes detail our current progress in showing such a result for different values of $s$. We showed the following useful representation of $R_{s,n}(f)$ in the \emph{8.7.19} Notes. For $k = (k_1,\ldots,k_n) \in [n]^s$, recursively defined the graph difference operator $D_k$ by 
\begin{equation*}
D_{k_1}f(x) = (f(x_{k_1}) - f(x))K_r(x_{k_1},x),~~ D_kf(x) = \bigl(D_{k_1}(D_{(k_2,\ldots,k_n)}f\bigr)(x)
\end{equation*}
Then when $s$ is even, letting $q = s/2$ we have
\begin{equation}
\label{eqn:roughness_functional_representation_even}
R_{s,n}(f) = \frac{1}{n}\sum_{i = 1}^{n} \left(\frac{1}{(nr^2)^q}\sum_{k \in [n]^q} D_kf(x_i)\right)^2
\end{equation}
and when $s$ is odd, letting $q = (s - 1)/2$ we have
\begin{equation}
\label{eqn:roughness_functional_representation_odd}
R_{s,n}(f) =  \frac{1}{2n^2r^2}\sum_{i,j = 1}^{n}\left(\frac{1}{(nr^2)^q}\sum_{k \in [n]^q}\bigl(D_kf(x_i) - D_kf(x_j)\bigr)\right)^2K_r(x_i,x_j)
\end{equation}
We have already obtained the desired bound on the 1st-order roughness functional $R_{1,n}(f)$, for any $f \in W_d^{1}(L)$, all scalings $r = r(n)$, and the uniform kernel. We therefore begin these notes with the case $s = 2$.

\section{Bounding the 2nd-Order Roughness Functional}
The (first and) second order roughness functionals are somewhat special. These roughness functionals do not involve taking compositions of the difference operator $D_k$, and as a result, we get the desired bounds in expectation even when $r(n)$ is small. 
\begin{lemma}
	\label{lem:2nd_order_roughness_functional}
	Fix $L > 0$, and form the neighborhood graph $G_{n,r}$ using kernel $K(z) = \1\{z^2 \leq r^2\}$. Suppose $f \in C^2(L)$ and $p \in C^1(L)$. Then for any $r(n) \geq n^{-1/(2+d)}$ and , we have
	\begin{equation*}
	\Ebb(R_{2,n}(f)) = O(L^2)
	\end{equation*}
\end{lemma}

\section{Bounding the 3rd-Order Roughness Functional}

\section{\textcolor{red}{Bounding the Roughness Functional in Expectation}}

\textcolor{red}{WARNING:} The following Lemma is not proved, but it is the result I am trying to prove. After the Lemma is stated, I go into some detail about how I intend to prove it.

For an integer $\ell > 0$, we will say $K$ is an order-$\ell$ kernel
\begin{equation*}
\int K(z) = 1 ~~\textrm{and}~~\int z^j K(z) = 0,~~\textrm{for $j = 1,\ldots,\ell$}
\end{equation*}
and further $K$ is $\ell$ times continuously differentiable with $K^{j}(z) = O(z^j K(z))$ for $j = 1,\ldots,s$.

\begin{lemma}
	\label{lem:roughness_functional_expectation}
	Suppose $f \in C^{s}(L)$ for some $s,L > 0$, and further suppose $p \in C^{\ell}(L)$ for $\ell = \floor{s}$ the largest integer strictly less than $s$. For any order-$\ell$ kernel $K$ and any $1 \geq r(n) \geq n^{-1/(2(s - 1)+d)}$, we have that
	\begin{equation*}
	\Ebb(R_{s,n}(f)) = O(1)
	\end{equation*} 
\end{lemma}
When $s \geq 3$ the graph Laplacian approximates higher-order derivatives by composing difference operators. The crudeness of this approximation means that in Lemma~\ref{lem:roughness_functional_expectation} we allow for a slower scaling of $r(n)$ than we did in Lemmas~\ref{lem:2nd_order_roughness_functional} and~\ref{lem:3rd_order_roughness_functional}. At a high level, however, we prove Lemma~\ref{lem:roughness_functional_expectation} in a similar fashion to Lemma~\ref{lem:2nd_order_roughness_functional}. We first break the sum into cases according to the number of unique indices, then bound the expectation case by case. 
The following Lemma will be the workhorse which supplies a sufficient bound in each case.
\begin{lemma}
	\label{lem:expected_difference_operators}
	Let $q = s/2$ when $s$ is even, and $q = (s - 1)/2$ when $s$ is odd. Under the same conditions as Lemma~\ref{lem:roughness_functional_expectation}, for any indices $k = (k_1,\ldots,k_q)$ and $\ell = (\ell_1,\ldots,\ell_q)$, we have
	\begin{equation}
	\label{eqn:expected_difference_operators_1}
	\Ebb(D_kf(x_i) D_\ell f(x_i)) =
	\begin{cases*}
	O(r^{2s}), & ~~\textrm{if all indices are distinct} \\
	O(r^{2} r^{d(\abs{k \cup \ell \cup i} - (2q + 1))}), & ~~\textrm{otherwise}~ 
	\end{cases*}
	\end{equation}
	Additionally, we have
	\begin{equation}
	\label{eqn:expected_difference_operators_2}
	\Ebb(d_iD_kf(x_j) d_iD_\ell f(x_j)) =
	\begin{cases*}
	O(r^{2s}), & ~~\textrm{if all indices are distinct} \\
	O(r^{2} r^{d(\abs{k \cup \ell \cup i \cup j} - (2q + 2))}), & ~~\textrm{otherwise}~ 
	\end{cases*}
	\end{equation}
\end{lemma}

@@

@@

\section{Proof of Lemma~\ref{lem:3rd_order_roughness_functional}}
We prove Lemma~\ref{lem:3rd_order_roughness_functional} when $d = 1$ and $r(n) \geq n^{-1/5}$.

@@

\paragraph{Case 4: $i,k,\ell$ all distinct.}
We rewrite the summand as $d_i(D_{\ell}f(x_j)) d_i(D_{k}f(x_j))K_r(x_i,x_j)$. Noting that
\begin{equation*}
d_i(D_{k}f(x_j)) = [f(x_k) - f(x_i)]K_r(x_k,x_i) -  [f(x_k) - f(x_j)]K_r(x_k,x_j)
\end{equation*}
by Lemma~\ref{lem:leading_term} we have that
\begin{equation*}
\abs{\Ebb(d_i(D_{k}f(x_j))|x_i,x_j)} \leq 2Lr^3.
\end{equation*}
Therefore,
\begin{align*}
\abs{\Ebb(d_i(D_{\ell}f(x_j)) d_i(D_{k}f(x_j))K_r(x_i,x_j))} & \leq \Ebb\biggl(\abs{\Ebb(d_k(D_{\ell}f(x_j))|x_i,x_j)\cdot\Ebb(d_k(D_{\ell}f(x_j))|x_i,x_j)\cdot K_r(x_k,x_j)}\biggr) \\
& \leq 4L^2r^6 \Ebb(\abs{K_r(x_k,x_j)}) \leq 4CL^2r^6.
\end{align*}
Since there are order $n^4$ terms in the summation for which $i,j,k$ and $\ell$ are all distinct, we have that
\begin{equation*}
\frac{1}{2n^4r^6} \sum_{i \neq j \neq k \neq \ell}^{n} \Ebb(D_{ik}f(x_j) d_iD_{\ell}f(x_j) K_r(x_i,x_j)) \leq 4C.
\end{equation*}
The above four cases cover all terms in the summation, and so we have proved Lemma~\ref{lem:3rd_order_roughness_functional}.
\section{Proof of Lemma~\ref{lem:expected_difference_operators}}

Since $f \in C^1(L)$, for all index vectors $k,\ell \in [n]^q$ and indices $i \in [n]$, the product of iterated difference operators $D_kf(x_i) D_{\ell}f(x_i)$ satisfies
\begin{equation*}
\abs{D_kf(x_i) D_{\ell}f(x_i)} \leq 4^{q} L^2 r^{2 - 2q}
\end{equation*}
Moreover $D_kf(x_i) D_{\ell}f(x_i)$ will equal zero if there exists $x_j, j \in k \cup \ell \cup i$ such that
\begin{equation*}
\norm{x_j - x_h} > r,~~\textrm{for all $h \in k \cup \ell \cup i$}
\end{equation*}
Therefore $D_kf(x_i) D_{\ell}f(x_i)$ is nonzero with probability $O(r^{\abs{k \cup \ell \cup i} - 1})$, which along with the boundedness of $D_kf(x_i) D_{\ell}f(x_i)$ implies the claimed result.

By the law of iterated expectation, we have
\begin{align}
\Ebb\left[D_kf(x_i)D_{\ell}f(x_i)\right] & = \Ebb\left[\Ebb\left(D_kf(x)|x_i = x\right) \Ebb\left(D_{\ell}f(x)|x_i = x\right)\right] \nonumber \\
& = \Ebb\left[\Ebb\left(D_kf(x)|x_i = x\right)^2\right] \label{eqn:expected_difference_operators_pf1}
\end{align}
Again applying the law of iterated expectation, letting $g$ be the function given by $g(x) = \Ebb(D_1f(x))$, we have
\begin{align*}
\Ebb(D_kf(x)) & = \Ebb(\Ebb(D_{k}f(x)|x_{k_1},\ldots,x_{k_{q-1}})) \\
& = \Ebb((D_{k_1\cdots k_{q - 1}}g)(x)).
\end{align*}
By Lemma~\ref{lem:leading_term}, we have that $g(x) = O(r^s)$ for all values of $x$, and therefore
\begin{equation*}
(D_{k_1\cdots k_{q_1}}g)(x) = O(r^{s - d(q - 1)})
\end{equation*}
Since $(D_{k_1\cdots k_{q_1}}g)(x)$ is nonzero with probability $O(r^{d(q - 1)})$, we have that 
\begin{equation*}
\Ebb(D_kf(x)) = \Ebb((D_{k_1\cdots k_{q - 1}}g)(x)) = O(r^s),
\end{equation*}
and the desired result follows from~\eqref{eqn:expected_difference_operators_pf1}.

The proof of~\eqref{eqn:expected_difference_operators_2} is essentially the same, and we do not reproduce it here.
\section{Auxiliary Results.}
\begin{lemma}
	\label{lem:difference_operator_taylor}
	When $f \in C^s(L)$, for any $k \in [n]$ 
	\begin{equation*}
	D_kf(x) = \left(\sum_{r = 1}^{s - 1} (x_k - x)^r f^{(r)}(x) + O((x_k - x)^{s})\right) \cdot K_r(x_k,x)
	\end{equation*}
\end{lemma}

\begin{lemma}
	\label{lem:leading_term}
	When $f \in C^s(L)$ and $p \in C^{s - 1}(L)$, we have that 
	\begin{equation*}
	\Ebb(\left(f(x_{\ell}) - f(x)\right)K_r(x_{\ell},x)) \leq Lr^s.
	\end{equation*}
\end{lemma}

>>>>

In this week's notes, we will focus our attention on upper bounding the roughness functional $R_{n,s}(f)$. Our main results should take the following form: when (a) $f \in C^{s}(L)$ for a fixed constant $L$ (or more ideally $f \in \mathcal{W}^{s}(L)$), (b) the neighborhood graph radius $r = r(n)$ is properly chosen as a function of $n$, and (c) $K$ is an appropriately chosen kernel, the roughness functional satisfies
\begin{equation}
\label{eqn:roughness_functional_bound}
\mathbb{E}\left[R_{s,n}(f)\right] = O\left(1\right)
\end{equation}
uniformly over all $f \in C^{s}(1)$. 
These notes detail our current progress in showing such a result for different values of $s$. We showed the following useful representation of $R_{s,n}(f)$ in the \emph{8.7.19} Notes. For $k = (k_1,\ldots,k_n) \in [n]^s$, recursively defined the graph difference operator $D_k$ by 
\begin{equation*}
D_{k_1}f(x) = (f(x_{k_1}) - f(x))K_r(x_{k_1},x),~~ D_kf(x) = \bigl(D_{k_1}(D_{(k_2,\ldots,k_n)}f\bigr)(x)
\end{equation*}
Then when $s$ is even, letting $q = s/2$ we have
\begin{equation}
\label{eqn:roughness_functional_representation_even}
R_{s,n}(f) = \frac{1}{n}\sum_{i = 1}^{n} \left(\frac{1}{(nr^2)^q}\sum_{k \in [n]^q} D_kf(x_i)\right)^2
\end{equation}
and when $s$ is odd, letting $q = (s - 1)/2$ we have
\begin{equation}
\label{eqn:roughness_functional_representation_odd}
R_{s,n}(f) =  \frac{1}{2n^2r^2}\sum_{i,j = 1}^{n}\left(\frac{1}{(nr^2)^q}\sum_{k \in [n]^q}\bigl(D_kf(x_i) - D_kf(x_j)\bigr)\right)^2K_r(x_i,x_j)
\end{equation}

\section{Bounding the Roughness Functional in Expectation}

For an integer $\ell > 0$, we will say $K$ is a $2$nd-order kernel if it is bounded and compactly supported on $B(0,1)$ and additionally
\begin{equation*}
\int K(z) = 1 ~~\textrm{and}~~\int z K(z) = 0
\end{equation*}
That $K$ be a $2$nd-order kernel is crucial for $L_n$ to act as a $2$nd-order differential operator, and for $R_{s,n}$ to scale at the proper rate.

\begin{lemma}
	\label{lem:roughness_functional_expectation}
	Suppose $f \in C^{s}(L)$ for some positive integer $s$ and $L > 0$, and further suppose $p \in C^{\ell}(L)$ for $\ell = \floor{s}$ the largest integer strictly less than $s$. For any $2$nd-order kernel $K$ and any $1 \geq r(n) \geq n^{-1/(2(s - 1)+d)}$, we have that
	\begin{equation*}
	\Ebb(R_{s,n}(f)) = O(1),
	\end{equation*} 
	uniformly over all $f \in C^{s}(L)$.
\end{lemma}

Note that Lemma~\ref{lem:roughness_functional_expectation} implies a high-probability bound on $R_{s,n}(f)$ by Markov's inequality. To prove Lemma~\ref{lem:roughness_functional_expectation}, we first break the sum~\eqref{eqn:roughness_functional_representation_even} (or ~\eqref{eqn:roughness_functional_representation_odd}) into cases according to the number of unique indices, then bound the expectation case by case. The following Lemma will be the workhorse which supplies a sufficient bound in each case.
\begin{lemma}
	\label{lem:expected_difference_operators}
	Let $q = s/2$ when $s$ is even, and $q = (s - 1)/2$ when $s$ is odd. Under the same conditions as Lemma~\ref{lem:roughness_functional_expectation}, for any indices $k = (k_1,\ldots,k_q)$ and $\ell = (\ell_1,\ldots,\ell_q)$, we have
	\begin{equation}
	\label{eqn:expected_difference_operators_1}
	\Ebb(D_kf(x_i) D_\ell f(x_i)) =
	\begin{cases*}
	O(r^{2s}), & ~~\textrm{if all indices are distinct} \\
	O(r^{2} r^{d(\abs{k \cup \ell \cup i} - (2q + 1))}), & ~~\textrm{otherwise}~ 
	\end{cases*}
	\end{equation}
	Additionally, we have
	\begin{equation}
	\label{eqn:expected_difference_operators_2}
	\Ebb(d_iD_kf(x_j) d_iD_\ell f(x_j)) =
	\begin{cases*}
	O(r^{2s}), & ~~\textrm{if all indices are distinct} \\
	O(r^{2} r^{d(\abs{k \cup \ell \cup i \cup j} - (2q + 2))}), & ~~\textrm{otherwise}~ 
	\end{cases*}
	\end{equation}
\end{lemma}

The minimum scaling condition $r(n) \geq n^{-1/(2(s - 1) + d)}$ is needed in order to ensure the diagonal terms of the sums in~\eqref{eqn:roughness_functional_representation_even} and~\eqref{eqn:roughness_functional_representation_odd} (where not all indices are distinct) do not dominate the off-diagonal terms (where all indices are distinct).

@@

\section{Proof of Lemma~\ref{lem:expected_difference_operators}}

Since $f \in C^1(L)$, for all index vectors $k,\ell \in [n]^q$ and indices $i \in [n]$, the product of iterated difference operators $D_kf(x_i) D_{\ell}f(x_i)$ satisfies
\begin{equation*}
\abs{D_kf(x_i) D_{\ell}f(x_i)} \leq 4^{q} L^2 r^{2 - ds}
\end{equation*}
Moreover $D_kf(x_i) D_{\ell}f(x_i)$ will equal zero if there exists $x_j, j \in k \cup \ell \cup i$ such that
\begin{equation*}
\norm{x_j - x_h} > r,~~\textrm{for all $h \in k \cup \ell \cup i$}
\end{equation*}
Therefore $D_kf(x_i) D_{\ell}f(x_i)$ is nonzero with probability $O(r^{d(\abs{k \cup \ell \cup i} - 1)})$, which along with the boundedness of $D_kf(x_i) D_{\ell}f(x_i)$ implies the claimed result.

By the law of iterated expectation, we have
\begin{align}
\Ebb\left[D_kf(x_i)D_{\ell}f(x_i)\right] & = \Ebb\left[\Ebb\left(D_kf(x)|x_i = x\right) \Ebb\left(D_{\ell}f(x)|x_i = x\right)\right] \nonumber \\
& = \Ebb\left[\Ebb\left(D_kf(x)|x_i = x\right)^2\right] \label{eqn:expected_difference_operators_pf1}
\end{align}
The result then follows from Lemma~\ref{lem:leading_term}.

The proof of~\eqref{eqn:expected_difference_operators_2} when some index is repeated is essentially the same, and we do not reproduce it.

When all indices $\ell,k,i$ and $j$ are distinct, by Lemma~\ref{lem:leading_term} there exists some $f_{s-1} \in C^1(L)$ such that
\begin{align*}
\Ebb(d_iD_kf(x_j)d_iD_{\ell}f(x_j)K_r(x_i,x_j)) & = \Ebb\biggl(\Bigl(d_i\bigl(O(r^{s-1})\cdot f_{s - 1} + O(r^s)\bigr)\Bigr)^2K_r(x_i,x_j)\biggr) \\
& = O(r^{2s - 2})\Ebb\Bigl(\bigl(d_if_{s-1}(x_j))\bigr)^2K_{r}(x_i,x_j)\Bigr) + O(r^{2s - 1})\Ebb\bigl(D_if_{s - 1}(x_j)\bigr)+ O(r^{2s})
\end{align*}
where the second equality follows from the linearity of the difference operator. Then since $f_{s-1} \in C^1(L)$, we have $\Ebb(D_if_{s-1}(x_j)) = O(r)$, and
\begin{equation*}
\Ebb\Bigl(\bigl(d_if_{s-1}(x_j))\bigr)^2K_{r}(x_i,x_j)\Bigr) = \Ebb\Bigl(\bigl(O(r)\bigr)^2K_{r}(x_i,x_j)\Bigr) = O(r^2),
\end{equation*}
establishing $\Ebb(d_iD_kf(x_j)d_iD_{\ell}f(x_j)K_r(x_i,x_j)) = O(r^{2s})$ as claimed.
\section{Auxiliary Results.}
\begin{lemma}
	\label{lem:difference_operator_taylor}
	When $f \in C^s(L)$, for any $k \in [n]$ 
	\begin{equation*}
	D_kf(x) = \left(\sum_{r = 1}^{s - 1} (x_k - x)^r f^{(r)}(x) + O((x_k - x)^{s})\right) \cdot K_r(x_k,x)
	\end{equation*}
\end{lemma}

\begin{lemma}
	\label{lem:leading_term}
	Suppose $f \in C^s(L)$, $p \in C^{s-1}(L)$, $k \in [n]^q$ for some $q \geq 1$, and that $K_r$ is a $2$nd-order kernel. Then if $2q \leq s - 1$,
	\begin{equation}
	\label{eqn:leading_term}
	\Ebb(D_kf(x)) = \sum_{\ell = 2q}^{s - 1} O(r^{\ell}) \cdot f_{\ell}(x) + O(r^s),
	\end{equation}
	for some $f_{\ell} \in C^{s - \ell}(L)$. If $2q \geq s$, $\Ebb(D_kf(x)) = O(r^s)$.  All $O(\cdot)$ terms may depend $L$ and $s$, but do not depend on $f$ or $x$.
\end{lemma}
\begin{proof}
	We will prove Lemma~\ref{lem:leading_term} in the case where $d = 1$. When $d \geq 2$, using multivariate Taylor expansions we find the same result, but with more notational overhead.

	We will prove by induction on $q$ in the case where $d = 1$. The When $q = 1$ and $k \in [n]$, by taking Taylor expansions of $f$ and $p$, we obtain
	\begin{align}
	\nonumber 
	\Ebb(D_kf(x)) & = \sum_{\ell = 1}^{s - 1} f^{(\ell)}(x) \int (z - x)^{\ell} K_r(z,x) p(z) dz + O(r^s) \\ 
	& = \sum_{\ell = 1}^{s - 1} \sum_{a = 0}^{s - 1} f^{(\ell)}(x) p^{(a)}(x) \underbrace{\int(z - x)^{\ell + a} K_r(z,x) dz}_{:=I_{t + a}} + O(r^s) \label{eqn:leading_term_pf1}
	\end{align}
	Since $K$ is a $2$nd-order kernel, $I_{1} = 0$ and $I_t = O(r^{t})$ for $t \geq 2$.  Additionally, when $\ell + a \leq s - 1$, we have that $f^{(\ell)}p^{(a)} \in C^{\min\{s - \ell, s - 1 - a\}} \subseteq C^{s - (\ell + a)}$, and $\abs{f^{(\ell)}p^{(a)}} \leq L^2$ for any $\ell$ and $a$. We can therefore simplify~\eqref{eqn:leading_term_pf1} by combining all terms where $\ell + a = t$, obtaining
	\begin{equation}
	\label{eqn:leading_term_pf2}
	\Ebb(D_kf(x)) = \sum_{t = 1}^{s - 1} f_t(x) I_t + O(r^s) = \sum_{t = 2}^{s - 1} f_t(x) I_t + O(r^s),
	\end{equation}
	which establishes~\eqref{eqn:leading_term} in the base case.

	Now, we assume \eqref{eqn:leading_term} holds for all $k \in [n]^q$, and prove the desired estimate on $\Ebb(D_{kj}f(x))$ for each $j \in [n]$. By the law of iterated expectation and~\eqref{eqn:leading_term_pf2},
	\begin{align*}
	\Ebb(D_{kj}f(x)) & = \Ebb(D_k(\Ebb(D_jf))(x)) \\
	& = \Ebb\left(D_k\left(\sum_{t = 2}^{s - 1} I_t f_t + O(r^s)\right)(x)\right) \\
	& = \sum_{t = 2}^{s - 1} I_t \cdot \Ebb(D_kf_t(x)) + O(r^s)
	\end{align*}
	where the second equality follows from the linearity and boundedness of $f \mapsto \Ebb(D_kf)$. We now apply the inductive hypothesis to $\Ebb(D_kf_t(x))$. If $2(q + 1) \geq s$, note that since $f_t \in C^{s - t}(L)$ for $t \geq 2$, we have by hypothesis $\Ebb(D_kf_t(x)) = O(r^{s - t})$. As a result
	\begin{equation*}
	\sum_{t = 2}^{s - 1} I_t \cdot \Ebb(D_kf_t(x)) = \sum_{t = 2}^{s - 1} I_t \cdot O(r^{s - t}) = O(r^s)
	\end{equation*} 
	Otherwise $2(q + 1) \leq s - 1$. For each $t = 2,\ldots, s - 1$, if additionally  $2q \leq s - t - 1$, then by hypothesis $\Ebb(D_kf_t(x)) = \sum_{\ell = 2q}^{s - t - 1} O(r^{\ell}) \cdot g_{\ell}(x) + O(r^{s - t})$ for some $g_{\ell} \in C^{s - t - \ell}(L)$, and otherwise $\Ebb(D_kf_t(x)) = O(r^{s - t})$. Therefore,
	\begin{align*}
	\sum_{t = 2}^{s - 1} I_t \cdot \Ebb(D_kf_t(x)) & = \sum_{t = 2}^{s - 1 - 2q} I_t \cdot \left\{\sum_{\ell = 2q}^{s - t - 1} O(r^{\ell}) \cdot g_{\ell}(x) + O(r^{s - t}) \right\} + \sum_{t = s - 1 - 2q}^{s - 1}I_{t} \cdot O(r^{s - t}) \\
	& = \sum_{t = 2}^{s - 1 - 2q} I_t \cdot \left\{\sum_{\ell = 2q}^{s - t - 1} O(r^{\ell}) \cdot g_{\ell}(x)\right\}  + O(r^s) \\
	& = \sum_{\ell = 2q}^{s - 3} \sum_{t = 2}^{s - \ell - 1} I_t \cdot O(r^{\ell}) \cdot g_{\ell}(x) + O(r^s).
	\end{align*}
	Noting that $g_{\ell} \in C^{s - (t + \ell)}(L)$ for some $\ell + t = 2(q + 1),\ldots,s - 1$, and $I_t \cdot O(r^{\ell}) = O(r^{t + \ell})$, we can rewrite the final equation as a sum over $\ell + t = 2(q + 1),\ldots,s - 1$, which proves~\eqref{eqn:leading_term}.
\end{proof}

\section{Old Work}

\subsection{Bounding the 2nd-Order Roughness Functional}
The (first and) second order roughness functionals are somewhat special. These roughness functionals do not involve taking compositions of the difference operator $D_k$, and as a result, we get the desired bounds in expectation even when $r(n)$ is small. 
\begin{lemma}
	\label{lem:2nd_order_roughness_functional}
	Fix $L > 0$, and form the neighborhood graph $G_{n,r}$ using kernel $K(z) = \1\{z^2 \leq r^2\}$. Suppose $f \in C^2(L)$ and $p \in C^1(L)$. Then for any $r(n) \geq n^{-1/(2+d)}$ and , we have
	\begin{equation*}
	\Ebb(R_{2,n}(f)) = O(L^2)
	\end{equation*}
\end{lemma}

\subsection{Bounding the 3rd-Order Roughness Functional}

@@

\subsection{Proof of Lemma~\ref{lem:3rd_order_roughness_functional}}
We prove Lemma~\ref{lem:3rd_order_roughness_functional} when $d = 1$ and $r(n) \geq n^{-1/5}$.

@@

\paragraph{Case 4: $i,k,\ell$ all distinct.}
We rewrite the summand as $d_i(D_{\ell}f(x_j)) d_i(D_{k}f(x_j))K_r(x_i,x_j)$. Noting that
\begin{equation*}
d_i(D_{k}f(x_j)) = [f(x_k) - f(x_i)]K_r(x_k,x_i) -  [f(x_k) - f(x_j)]K_r(x_k,x_j)
\end{equation*}
by Lemma~\ref{lem:leading_term} we have that
\begin{equation*}
\abs{\Ebb(d_i(D_{k}f(x_j))|x_i,x_j)} \leq 2Lr^3.
\end{equation*}
Therefore,
\begin{align*}
\abs{\Ebb(d_i(D_{\ell}f(x_j)) d_i(D_{k}f(x_j))K_r(x_i,x_j))} & \leq \Ebb\biggl(\abs{\Ebb(d_k(D_{\ell}f(x_j))|x_i,x_j)\cdot\Ebb(d_k(D_{\ell}f(x_j))|x_i,x_j)\cdot K_r(x_k,x_j)}\biggr) \\
& \leq 4L^2r^6 \Ebb(\abs{K_r(x_k,x_j)}) \leq 4CL^2r^6.
\end{align*}
Since there are order $n^4$ terms in the summation for which $i,j,k$ and $\ell$ are all distinct, we have that
\begin{equation*}
\frac{1}{2n^4r^6} \sum_{i \neq j \neq k \neq \ell}^{n} \Ebb(D_{ik}f(x_j) d_iD_{\ell}f(x_j) K_r(x_i,x_j)) \leq 4C.
\end{equation*}
The above four cases cover all terms in the summation, and so we have proved Lemma~\ref{lem:3rd_order_roughness_functional}.
